Building Markov State Model for a Periodically Driven Non-Equilibrium System

### 2014-09-02 writedown/period.noneq.msm/paper.tex
add t-d prob of coresets

\begin{figure}
  \centering  
  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.40/fig-dist.eps}
  % \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-dist-msm.eps}
  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-1.eps}
  \caption{The steady state distribution calculated by brute force non-equilibrium is compared with that by the discretized dynamics.}
  \label{fig:num-1}
\end{figure}

@@

\begin{table}
  \centering
  \caption{
    The eigenvalue comparison
  }
  \begin{tabular*}{0.4\textwidth}{@{\extracolsep{\fill}}c rr}\hline\hline
      &  $\lambda_2$ & $\lambda_3$ \\\hline
    $P$         &0.907  &0.686        \\
    $\hat P$    &0.914  &0.744        \\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp1}
\end{table}

@@

>>>>

\begin{figure}
  \centering  
  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.40.steadyDist//fig-dist.eps}
  % \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-dist-msm.eps}
  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-1.eps}
  \caption{The steady state distribution calculated by brute force non-equilibrium is compared with that by the discretized dynamics.}
  \label{fig:num-1}
\end{figure}

@@

\begin{table}
  \centering
  \caption{
    The eigenvalue comparison
  }
  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}c rrr}\hline\hline
      &  $\lambda_2$ & $\lambda_3$ & $\lambda_4$ \\\hline
    $P$         &0.907  &0.686 & 0.553       \\
    $\hat P$    &0.914  &0.744 & --       \\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp1}
\end{table}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.40/fig-coreset-prob.eps}
  \caption{The time-dependent probability $\hat P_l$. Solid lines are from brute force MD simulation, while the dashed lines are from MSM.}
  \label{fig:num-7}
\end{figure}

We study the time-dependent expectation values of
the properties, i.e.
\begin{align}
  \mathcal A(t) = \langle A(i)\rangle_t = \sum_{i\in S} A(i) p(i,t),
\end{align}
which are linear combinations of the backward
committor, i.e.
\begin{align}
  A(i) = \sum_{l=1}^k \alpha_l q^\bwd_l(i)
\end{align}
then
\begin{align}\nonumber
  \mathcal A(t) &=
  \sum_{i\in S} \sum_{l=1}^k \alpha_l q^\bwd_l(i)  p(i,t) \\\nonumber
  & =
  \sum_{i\in S} \sum_{l=1}^k \alpha_l \prob (\hat X_t = l \vert X_t = i) \prob (X_t = i) \\\nonumber
  & =
  \sum_{i\in S} \sum_{l=1}^k \alpha_l \prob (\hat X_t = l ,X_t = i) \\\nonumber
  & =
  \sum_{l=1}^k \alpha_l \prob (\hat X_t = l) \\\label{eq:num-28}
  & =
   \sum_{l=1}^k \alpha_l \,\hat p (l, t),
\end{align}
where the time-dependent projected probability is governed by the MSM:
\begin{align}\label{eq:num-29}
  \hat p(i, t+T) = \sum_{j\in S} \hat p(j,t)\hat P_{ji}
\end{align}
In Fig.~\ref{fig:num-7} we compare the numerical calculation of $\hat p (l, mT), \ m\in\mathbb N$ from brute force and MSM calculations.
In the brute force calculation, the RHS terms on the projection $\hat p (l, mT) = \sum_{i\in S}  q^\bwd_l(i)  p(i,mT) $ are estimated from the
non-equilibrium MD simulations. For MSM, the projection for the initial probability is applied $\hat p (l, 0) = \sum_{i\in S}  q^\bwd_l(i)  p(i,0) $, then
the time-dependent probability at $mT$ is generated by Eq.~\eqref{eq:num-29}.
% The projected probability, e.g.~$\hat p (l', mT)$ is calculated
% by Eq.~\eqref{eq:num-28} letting $\alpha_l = \delta_{l'l}$.
